---
title: "Comparison of Outfall Monitoring Time Ranges"
author: "Tyler Nciekrson"
date: "February 17, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sp)
library(leaflet)
library(rgdal)
library(rgeos)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(stringr)
library(lubridate)
library(purrr)

dischargepoints <- readOGR(dsn = "Outfall_Prioritization.shp", layer = "swDischargePoint")
dischargepoints <- spTransform(dischargepoints, CRS("+proj=longlat"))

tributaries <- readOGR(dsn = "Outfall_Prioritization.shp", layer = "swDischargePoint_Tributary")
tributaries <- spTransform(tributaries, CRS("+proj=longlat"))

dis <- as_tibble(as.data.frame(lapply(dischargepoints@data, as.character), stringsAsFactors = F))
dis['x'] <- dischargepoints@coords[, 1]
dis['y'] <- dischargepoints@coords[, 2]

tri <- as_tibble(as.data.frame(lapply(tributaries@data, as.character), stringsAsFactors = F))

tridis <- tri %>%
  left_join(dis, by=c("Outfall_Tr" =  "FACILITYID")) %>%
  select(Outfall_Tr, HachFlow_2, x, y) %>%
  drop_na()

tridis <- as_tibble(as.data.frame(lapply(tridis, as.character), stringsAsFactors = F))

ggplot(data = tridis) + 
  geom_histogram(mapping = aes(x=HachFlow_2), stat='count') + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
  
start_end <- str_match(na.omit(tridis$HachFlow_2), '^([a-zA-z]{3}-\\s*\\d{1,2})\\s*-\\s*([a-zA-z]{3}-\\s*\\d{1,2}).*$')

start <- na.omit(start_end[,2])
end <- na.omit(start_end[,3])

date_range <- start_end[,1]
start <- paste0(gsub(' ', '', start), '-2016')
end <- paste0(gsub(' ', '', end), '-2016')


start <- as_date(start, format='%b-%d-%Y')
end <- as_date(end, format='%b-%d-%Y')
 
dates <- tibble(HachFlow_2=date_range, start=start, end=end, idx=1:length(start), date= start + days(as.integer(start - end)%/%2))

dis_dates <- dates %>%
  left_join(tridis) %>%
  group_by(Outfall_Tr) %>% 
  filter(row_number() == 1) %>%
  ungroup()

dis_dates[, 'code'] <- lapply(dis_dates[, 'Outfall_Tr'], function(x){
                    str_split(x, '0', simplify = T)[, 1]
                  })
```

## Outfall Monitoring Time ranges
A considerable hurdle in using the outfall prioritization data is the varying ranges of time for which data was collected. The design of the outfall prioritizatin study allowed for outfalls to be monitored over different ranges of time. Below is a plot of the time ranges for which each outfall was monitored. There is some overlap between monitorings, but these overlaps tend to be small. This makes analysis such as comparing the flow between outfall locations to determine attribution challenging.

```{r timeframes, echo=FALSE}
ggplot(data=dis_dates, mapping=aes(date, Outfall_Tr, xmin=start, xmax=end, color=code)) + geom_errorbarh()
```

The above chart only tells half of the story. Spacially, outfalls appear grouped by their code letter. 

```{r pressure, echo=FALSE}
pal <- colorFactor(
  palette = 'Set1',
  domain = dis_dates$code
)

leaflet() %>%
  setView(lng = -117.7, lat = 33.55, zoom = 11) %>%
  addTiles(option = providerTileOptions()) %>%
  addCircles(data = dis_dates, lng = ~x, lat = ~y, 
             color = ~pal(code), 
             radius = 20, opacity = 1.0,
             popup = paste0('Facility ID: ', dis_dates$Outfall_Tr, '<br>',
                            'Start: ', dis_dates$start, '<br>',
                            'End: ', dis_dates$end, '<br>')) %>%
  addLegend('bottomleft', pal = pal, 
            values =dis_dates$code, opacity = 1.0)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
